Synergistic retrievals of ice in high clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-08-22 RST/Submission/responseReviewers_Rev2.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage[margin=1in]{geometry}
\author{Mircea Grecu and John E. Yorks}
\title{Synergistic retrievals of ice in high clouds
Response to Reviewers}
\date{}
\begin{document}
\maketitle

\noindent \textbf{Reviewer 2}

\noindent \textbf{General Summary}

\noindent\textit{ 
For the sake of reproducibility, the authors should make all relevant source code publicly available. Furthermore, the data availability statement should clearly state which CloudSat products were used in the study.}\\

\noindent\textit{l. 23 - 24: Considering that the study neglects substantial uncertainties that will affect the accuracy of an actual synergistic retrieval, the sentence should mention that the 'significant improvements' were found under idealized conditions.}\\

\noindent Yes, we agree with the reviewer that the synergy was found under idealized conditions. We added a statement to this effect in the manuscript. Nevertheless, although additional work is likely needed to make optimal use of this synergy in practice, it is hard to envision how the tree instruments considered together cannot provide a more complete and quantitatively more accurate pictures than any one of them considered independently.\\

\noindent\textit{l. 85: You state that you use the 2C-ICE product to extend your CS-based estimates. However, you do not explain how.} \\

\noindent We apologize for the omission. When the CS-reflectivity is below the noise level, we use the IWC estimates in the 2C\-ICE product and $N_w$ derived by our statistical model. We added a sentence to the manuscript to clarify this point.\\

\noindent\textit{l. 113: Please introduce the variable H as relative height above freezing level.}\\

\noindent\textit{l. 125: I am confused by this paragraph. The preceding paragraph described how you parametrized $N_w$. However, $N_w$ still depends on $a_{norm}$, the calculation of which is described first in the following paragraph.}\\

\noindent We apologize for the confusion. No, $N_w$ does not depend on $a_{norm}$. $a_{norm}$ derived by regressing $log_{10}(IWC/N_w)$ against $log_{10}(Z/_Nw)$ with $Z$ in natural units. The slope of the regression is $b$ in Eq. (1), while $a_{norm}$ is $10^{intercept}$ where $intercept$ is the intercept of the regression.  This is explained in Testud et al. (2001) and several other papers using the concept of normalized PSDs. \\

\noindent\textit{l. 147: Here, you assume a fixed value for $N_w$. How is this consistent with the $N_w$ parametrization described earlier?}\\

\noindent We apologize for the confusion. As explained above, $IWC$ and $Z$ are normalized by $N_w$ in the derivation of $a_{norm}$. Consequently, the actual value of $N_w$ does not matter. One may set $N_w$ to the unit value. However, that would result in very unusual $IWC$ and $Z$, which would make sanity checks impossible.  We therefore set $N_w$ to a frequently used, but arbitrary values. This however does not have any impact on the actual value of $N_w$.\\

\noindent\textit{l. 258: How are absorption and extinction handled in your retrieval of IWC and PSD parameters from CS reflectivities?}\\

The gaseous absorption is modeled using the Rosenkranz (1993) model assuming the same water vapor, temperature and pressure profiles used in the lidar model and the radiative transfer calculations. The extinction is computed using the SSRGA theory, while the attenuation correction is handled through a forward attenuation correction procedure.
\\
\noindent\textit{l. 276 - 278: While generally true, this does not apply to this study since the test data stems from the same distribution as the a priori in either case.}\\

\noindent We just explain our preference for an observation-based dataset as opposed to a purely synthetic (CRM-based) dataset. However, we do not imply that our results are bias-free or that CRM can not eventually produce more complete and less-biased datasets. But until such datasets emerge, we consider the framework described .\\

\noindent\textit{l. 291 - 292: Are you using a two-layer neural network without activations functions, or is this a typo? In the former case, I suggest you use a deeper neural network with non-linearities for the classification as you model may be underfitting the data.}\\

\noindent We apologize for the confusion and omissions. The neural network has two hidden layers with ReLU activations. We considered additional layers and/or different numbers of neurons per layer, but the results did not improve. We added a sentence to the manuscript to clarify this point. \\

\noindent\textit{l. 347: The new distribution of retrieved gravity centers cannot be described as narrow.}

\noindent\textit{Section 3. b.: Please add results for the lidar-radar retrievals.}\\

\noindent\textit{Table 2: Please include NRMS also for IWP and gravity centers. Since you mention it in the text, I suggest to also include the correlation coefficient in the table.}\\

\noindent\textit{l. 440: The term cross-validation implies several iterations of evaluations. This is different from what you are doing here.}\\

\noindent We agree with the reviewer that our particular form of validation, which more generally known as hold-out validation, is not considered cross-validation by some authors. Nevertheless, other authors (e.g. Arlot 2010) consider hold-out the most basic form of cross-validation. To avoid controversy, 
we use term hold-out validation instead of cross-validation in the revised manuscript.\\

\begin{thebibliography}{999}

\bibitem{arlot2010survey}
Arlot, S., A survey of cross-validation procedures for model selection. Statistics Surveys. 2010, 4, 40-79.

\bibitem{ferreira2001}
Ferreira, F., P. Amayenc, S. Oury, and J. Testud, 2001: Study and Tests of Improved Rain Estimates from the TRMM Precipitation Radar. 
J. Appl. Meteor. Climatol., 40, 1878–1899, https://doi.org/10.

\end{thebibliography}

\end{document}

### 2023-08-22 RST/Submission/RSTManuscript_rev2.tex
rev 2

\abstract{ In this study, we investigate the synergy of elastic backscatter lidar, Ku-band radar, and sub-millimeter-wave radiometer measurements
in the retrieval of ice from satellite observations. The synergy is analyzed through the generation of a large dataset 
of Ice Water Content (IWC) profiles and simulated lidar, radar and radiometer observations. 
The characteristics of the instruments e.g. frequencies, sensitivities, etc. are set based on the expected characteristics 
of instruments of the Atmosphere Observing System (AOS) mission. A cross-validation methodology is used to assess the
accuracy of the IWC profiles retrieved from various combinations of observations from the three instruments. Specifically, the IWC and
associated observations are randomly divided into two datasets, one for training and the other for evaluation.
The training dataset is used to train the retrieval algorithm, while the evaluation dataset is used to assess the 
retrieval performance. The dataset of IWC profiles is derived from CloudSat 
reflectivity and CALIOP lidar observations.
The retrieval of the ice water content IWC profiles from the computed observations is achieved in two steps. 
In the first step, a class, out of 18 potential classes characterized by different vertical distribution of IWC, 
is estimated from the observations. The 18 classes are predetermined based on the k-Means clustering algorithm. 
In the second step, the IWC profile is estimated using an Ensemble Kalman Smoother (EKS) algorithm that uses the 
estimated class as a priori information.\\
The results of the study show that the synergy of lidar, radar, and radiometer observations is significant
in the retrieval of the IWC profiles.  The inclusion of the lidar backscatter observations in the retrieval process has a
larger impact on the retrieval performance than the inclusion of the radar observations. 
As ice clouds have a significant impact on atmospheric radiative processes, this
work is relevant to ongoing efforts to reduce uncertainties in climate analyses and projections.}

@@

The future NASA Atmospheric Observing System (AOS) mission \citep{braun2022} is expected to feature new 
combinations of observations that may be used to quantify the amounts of ice in high clouds and 
characterize the microphysical properties of ice particles. In the AOS terminology, high clouds are convectively
generated clouds \citep{braun2022}. They are the result of strong vertical mass transport accompanied by
horizontal transport of hydrometeors in the upper troposphere.  As high clouds are of paramount importance in
understanding the quantifying radiative processes, they constitute one of the AOS major objectives \citep{braun2022}.
To achieve its objectives, AOS will rely on a combination of active and passive observations onboard multiple spacecrafts
in two different orbits.  One of the orbits is expected to be polar, while the other is expected to be inclined, which
would allow the study of atmospheric processes at sub-daily time scales, with an emphasis on deep
convection, high clouds, and aerosols \citep{braun2022,yorks2022}.
The AOS inclined observations will include backscatter
from an elastic backscatter lidar \citep{weitkamp2006},
Ku-band radar reflectivity, and submillimeter wave radiometer brightness temperature measurements. 
While not necessarily optimal for cloud ice estimation, these measurements are 
complimentary and enable the synergistic characterization of ice clouds. 
That is, despite the fact that lidar observations 
attenuate quickly in thick ice clouds and the Ku-band radar will not be able to detect clouds 

@@

that may be incorporated into the radiometer retrievals. Herein, the term retrieval is defined as the 
process of estimating geophysical variables from remote sensing observations.

@@

incorporating lidar and radar observations into the radiometer retrieval of ice clouds.
Because the existing amount of coincident backscatter lidar, Ku-band radar, and submillimeter-wave 
radiometer observations is rather insufficient to derive conclusive results, we employ accurate 
physical models to simulate lidar, radar and radiometer observations and use a cross-validation 
methodology to characterize the retrieval accuracy. As estimates from passive instrument 
observations strongly depend on "a priori" information \citep{rodgers2000inverse}, for results to be 
relevant in real applications, it is necessary to base them on realistic vertical distributions of 
ice properties.  Such distributions may be derived from cloud-resolving-model (CRM) simulations 
\citep{pfreundschuh2020synergistic,liu2022assessing} or directly from observations.  In this study, we employ the latter 
approach, as CRMs may still be deficient in properly reproducing the vertical distribution of ice 
clouds and their associated microphysical properties.  Specifically, we use observations and
products from the CloudSat (CS) mission (Stephens et al. 2002) to derive a database of ice microphysical
properties and associated simulated lidar, radar, and radiometer observations.  To account for variability in 
the Particle Size Distributions (PSD) that may not be well represented in the 2C-ICE product, we use a simple
but effective approach to perturb the PSD generalized intercepts from their nominal values.
The resulting database is used to
investigate the accuracy of estimated ice cloud properties from the simulated observations. Another major
difference relative to previous studies is the unique combination of instruments investigated herein. It should be
mentioned that although based on observations rather than CRM simulations, the approach used in this study is

@@

good first step towards the development of an operational synergistic retrieval of ice clouds from AOS inclined observations.
The article is organized as follows.  In Section 2, we describe the approach used to derive the ice properties and
the associated simulated observations, the retrieval and the evaluation methodology.  In Section 3, we 
present the results of the evaluation methodology. We conclude in Section 4.

@@

    Instrument & Frequency/Wavelength & Noise Assumptions& Sensitivity \\
    \hline
    Lidar & 532 nm & LogNormal(0,0.1) & 5e-7 m$^{-1}$sr$^{-1}$ \\
    \hline
    Radar & 13.8 GHz & 0.5dB & 8 dBZ \\
    \hline
    Radiometer & 89 GHz & 1.0 K & N/A \\
    & 183.31+/-0.2 GHz & 1.0 K & N/A \\
    & 183.31+/-1.1 GHz & 1.0 K & N/A \\
    & 183.31+/-2.8 GHz & 1.0 K & N/A \\
    & 183.31+/-4.2 GHz & 1.0 K & N/A \\
    & 183.31+/-6.8 GHz & 1.0 K & N/A \\
    & 183.31+/-11 GHz & 1.0 K & N/A \\
    & 325.15+/-1.5 GHz & 1.0 K & N/A \\
    & 325.15+/-3.5 GHz & 1.0 K & N/A \\
    & 183.31+/-9.5 GHz & 1.0 K & N/A \\
   \hline \\

>>>>

\abstract{ In this study, we investigate the synergy of elastic backscatter lidar, Ku-band radar, and sub-millimeter-wave radiometer measurements
in the retrieval of ice from satellite observations. The synergy is analyzed through the generation of a large dataset 
of Ice Water Content (IWC) profiles and simulated lidar, radar and radiometer observations. 
The characteristics of the instruments e.g. frequencies, sensitivities, etc. are set based on the expected characteristics 
of instruments of the Atmosphere Observing System (AOS) mission. A cross-validation methodology is used to assess the
accuracy of the IWC profiles retrieved from various combinations of observations from the three instruments. Specifically, the IWC and
associated observations are randomly divided into two datasets, one for training and the other for evaluation.
The training dataset is used to train the retrieval algorithm, while the evaluation dataset is used to assess the 
retrieval performance. The dataset of IWC profiles is derived from CloudSat 
reflectivity and CALIOP lidar observations.
The retrieval of the ice water content IWC profiles from the computed observations is achieved in two steps. 
In the first step, a class, out of 18 potential classes characterized by different vertical distribution of IWC, 
is estimated from the observations. The 18 classes are predetermined based on the k-Means clustering algorithm. 
In the second step, the IWC profile is estimated using an Ensemble Kalman Smoother (EKS) algorithm that uses the 
estimated class as a priori information.\\
The results of the study show that the synergy of lidar, radar, and radiometer observations is significant in the retrieval of the IWC profiles.  Nevertheless, it should be mentioned that this synergy was found under idealized conditions, and additional work might be required to materialize it in practice. The inclusion of the lidar backscatter observations in the retrieval process has a larger impact on the retrieval performance than the inclusion of the radar observations. As ice clouds have a significant impact on atmospheric radiative processes, this work is relevant to ongoing efforts to reduce uncertainties in climate analyses and projections.}

@@

The future NASA Atmospheric Observing System (AOS) mission \citep{braun2022} is expected to feature new combinations of observations that may be used to quantify the amounts of ice in high clouds and characterize the microphysical properties of ice particles. In the AOS terminology, high clouds are convectively generated clouds \citep{braun2022}. They are the result of strong vertical mass transport accompanied by
horizontal transport of hydrometeors in the upper troposphere.  As high clouds are of paramount importance in understanding the quantifying radiative processes, they constitute one of the AOS major objectives \citep{braun2022}. To achieve its objectives, AOS will rely on a combination of active and passive observations onboard multiple spacecrafts in two different orbits.  One of the orbits is expected to be polar, while the other is expected to be inclined, which would allow the study of atmospheric processes at sub-daily time scales, with an emphasis on deep convection, high clouds, and aerosols \citep{braun2022,yorks2022}. The AOS inclined observations will include backscatter from an elastic backscatter lidar \citep{weitkamp2006}, Ku-band radar reflectivity, and submillimeter wave radiometer brightness temperature measurements. 
While not necessarily optimal for cloud ice estimation, these measurements are complimentary and enable the synergistic characterization of ice clouds. That is, despite the fact that lidar observations attenuate quickly in thick ice clouds and the Ku-band radar will not be able to detect clouds 

@@

that may be incorporated into the radiometer retrievals. Herein, the term retrieval is defined as the process of estimating geophysical variables from remote sensing observations.

@@

incorporating lidar and radar observations into the radiometer retrieval of ice clouds. Because the existing amount of coincident backscatter lidar, Ku-band radar, and submillimeter-wave  radiometer observations is rather insufficient to derive conclusive results, we employ accurate 
physical models to simulate lidar, radar and radiometer observations and use a cross-validation methodology to characterize the retrieval accuracy. As estimates from passive instrument observations strongly depend on "a priori" information \citep{rodgers2000inverse}, for results to be 
relevant in real applications, it is necessary to base them on realistic vertical distributions of ice properties.  Such distributions may be derived from cloud-resolving-model (CRM) simulations \citep{pfreundschuh2020synergistic,liu2022assessing} or directly from observations.  In this study, we employ the latter approach, as CRMs may still be deficient in properly reproducing the vertical distribution of ice clouds and their associated microphysical properties.  Specifically, we use observations and products from the CloudSat (CS) mission (Stephens et al. 2002) to derive a database of ice microphysical properties and associated simulated lidar, radar, and radiometer observations.  To account for variability in the Particle Size Distributions (PSD) that may not be well represented in the 2C-ICE product, we use a simple but effective approach to perturb the PSD generalized intercepts from their nominal values.
The resulting database is used to investigate the accuracy of estimated ice cloud properties from the simulated observations. Another major difference relative to previous studies is the unique combination of instruments investigated herein. It should be mentioned that although based on observations rather than CRM simulations, the approach used in this study is

@@

good first step towards the development of an operational synergistic retrieval of ice clouds from AOS inclined observations. The article is organized as follows.  In Section 2, we describe the approach used to derive the ice properties and the associated simulated observations, the retrieval and the evaluation methodology.  In Section 3, we present the results of the evaluation methodology. We conclude in Section 4.

@@

    Instrument & Frequency/Wavelength & Noise Assumptions& Sensitivity \\
    \hline
    Lidar & 532 nm & LogNormal(0,0.1) & 5e-7 m$^{-1}$sr$^{-1}$ \\
    \hline
    Radar & 13.8 GHz & 0.5dB & 8 dBZ \\
    \hline
    Radiometer & 89 GHz & 1.0 K & N/A \\
    & 183.31+/-0.2 GHz & 1.0 K & N/A \\
    & 183.31+/-1.1 GHz & 1.0 K & N/A \\
    & 183.31+/-2.8 GHz & 1.0 K & N/A \\
    & 183.31+/-4.2 GHz & 1.0 K & N/A \\
    & 183.31+/-6.8 GHz & 1.0 K & N/A \\
    & 183.31+/-11 GHz & 1.0 K & N/A \\
    & 325.15+/-1.5 GHz & 1.0 K & N/A \\
    & 325.15+/-3.5 GHz & 1.0 K & N/A \\
    & 325.15+/-9.5 GHz & 1.0 K & N/A \\
   \hline \\
